Attack-Tolerance in Structured Networks via Multipath Routing \\ Draft: 2016-02-18

### 2016-02-21 ec-2016/source/paper.tex
Add table for algorithm parameters.

@@

>>>>

\subsection{Butterfly Network Topology}

@@

\subsection{Routing Algorithm: Overview}

This section gives an informal overview of the multipath routing algorithm.

\begin{table}%
\tbl{Butterfly Multipath Routing Variables\label{tab:routing}}
{
\begin{tabular}{|l|l|}
\hline
NAME & VARIABLE \\\hline
butterfly dimension & $m \in \mathbb{Z}_+$ \\\hline
trust radius & $h \in \mathbb{Z} : 1 \leq h \leq \lfloor m/2 \rfloor$ \\\hline
path index & $s \in \{0,1\}^h$ \\\hline
\end{tabular}
}
\end{table}%

\subsection{Routing Algorithm: Proof}
